### 2012-06-21 inst/examples/voi_sethi_parameters.Rmd
fixed tables for voi_sethi low noise

ggplot(policy) +
  geom_point(aes(stock, stock-x_grid[value], color=variable)) +
	geom_smooth(aes(stock, x_grid[value], color=variable)) +
  ylab("harvest")

@@

``` {r prettytable, cache=FALSE, results="asis"}
require(xtable)
uncertainties <- c("deterministic", "growth", "measure", "implement", "growth+measure", "growth+implement", "measure+implement", "all")
print(xtable(matrix(means$V1, nrow=7, dimnames=list(uncertainties, uncertainties))), type="html")
print(xtable(matrix(sds$V1, nrow=7, dimnames=list(uncertainties, uncertainties))), type="html")
````

>>>>

ggplot(policy) +
  geom_point(aes(stock, x_grid[value], color=variable)) +
	geom_smooth(aes(stock, x_grid[value], color=variable)) +
  ylab("harvest")

@@

``` {r prettytable, cache=FALSE, results="asis"}
require(xtable)
uncertainties <- c("deterministic", "growth", "measure", "implement", "growth+measure", "growth+implement", "all")
print(xtable(matrix(means$V1, nrow=7, dimnames=list(uncertainties, uncertainties))), type="html")
print(xtable(matrix(sds$V1, nrow=7, dimnames=list(uncertainties, uncertainties))), type="html")
````
